---
pagetitle: Josh Leon - Home
output:
  html_document:
    theme: journal
---

<html>
<head>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
```
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
  body {background-color:#d6c0a8;}
</style> 

<style>
div.white {background-color:#ffffff;}
</style>

<style>
h1 {color: black;
    font-size: 200%}
p  {color: black;
    font-size: 125%}
a {font-size: 115%}
a:link {
  color: #ffffff;
  background-color: transparent;
  text-decoration: none;
}
a:visited {
  color: #ffffff;
  background-color: transparent;
  text-decoration: none;
}
a:hover {
  color: coral;
  background-color: transparent;
  text-decoration: underline;
}
a:active {
  color: coral;
  background-color: transparent;
  text-decoration: underline;
  font-size: 125%;
}
ul {
  list-style-type: none;
  margin: 0;
  padding: 0;
  overflow: hidden;
  background-color: #36454F;
  position: fixed;
  top: 0;
  width: 100%;
}

li {
  float: left;
  border-right: 1px solid #ffffff;
}

li:last-child {
  border-right: none;
}

li a {
  display: block;
  color: white;
  text-align: center;
  padding: 14px 16px;
  text-decoration: none;
}

li a:hover {
  background-color: #111;
}
.active {
  background-color: #04AA6D;
}
</style>

<ul>
  <li><a href="http://JLEON123.github.io">Homepage</a></li>
  <li><a href="http://JLEON123.github.io/portfolio/">Data Analytics</a></li>
  <li><a href="http://JLEON123.github.io/Research/index.html">Research</a></li>
  <li><a href="http://JLEON123.github.io">Conferences</a></li>
  <li><a href="http://JLEON123.github.io">Publications</a></li>
  <li><a href="http://JLEON123.github.io">CV</a></li>
</ul>

</head>

<body>
In progress
```{r image-ref-for-in-text, echo = FALSE, message=FALSE, fig.align='center'}
knitr::include_graphics("./Josh_Leon_CV.pdf")
```
</body>
</html>
